Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-11 paper-ieee-trans.tex
P3 C2 L29 reviewer#1 jargon removed

In the following sections, we describe the three main pillars that sustain the project's strategy to attain reliability throughout the
% Comment
%%P3 C2 L29: This introductory paragraph goes into a bit too much jargony detail, I think, especially given that it is followed by in-depth coverage of each "pillar". I suggest a clearer identification of each pillar, maybe via bullets or definition paragraphs, avoiding or with general-audience definition of jargon like DevOps, delivery mechanisms, two-factor validation, pilot testbeds, and early adoption. I appreciate this may all be highly meaningful to someone steeped in this operational area, but to an interested outsider it reads much like management jargon -- particuarly the final sentence: is this a long-winded way of saying "used during the commissioning period"?
software lifecycle. A solid \textit{Software Quality Assurance (SQA) criteria
and metrics gathering definition} provides guidelines to develop quality
software, validating each change in the code, and facilitating its adoption. The software lifecycle is continuously monitored
by a set of metrics, allowing prompt reactions to detected malfunctions throughout the
process. A \textit{bottom--up adoption of DevOps principles} promotes automation to enable
the foregoing change--based development process and set up advanced delivery mechanisms.
The last key pillar is the \textit{two--factor validation} carried out over the project's pilot testbeds and
e--Infrastructure resource provider's early--adoption.

>>>>

In the following sections, we describe the three main pillars that sustain the project's strategy to attain reliability throughout the
% Comment
%%P3 C2 L29: This introductory paragraph goes into a bit too much jargony detail, I think, especially given that it is followed by in-depth coverage of each "pillar". I suggest a clearer identification of each pillar, maybe via bullets or definition paragraphs, avoiding or with general-audience definition of jargon like DevOps, delivery mechanisms, two-factor validation, pilot testbeds, and early adoption. I appreciate this may all be highly meaningful to someone steeped in this operational area, but to an interested outsider it reads much like management jargon -- particuarly the final sentence: is this a long-winded way of saying "used during the commissioning period"?
software lifecycle:
\begin{itemize}
    \item A solid \textit{Software Quality Assurance (SQA) criteria and metrics gathering definition} provides guidelines to develop quality
    software, validating each change in the code, and facilitating its adoption. The software lifecycle is continuously monitored
    by a set of metrics, allowing prompt reactions to detected malfunctions throughout the
    process. 
    \item The \textit{promotion of automation} to enable the foregoing change--based validation approach 
    and to accelerate the delivery process of new software versions.
    \item A post-release validation carried out over the project's \textit{preview testbeds}, where the new product versions
    are deployed as part of the integration validation, and the \textit{testing in production environments} by external resource providers.
\end{itemize}
